Thesis Draft

### 2015-09-28 chapter2.tex
format changed.
Former-commit-id: 268481e7bc2309b7a723363c8a58ad53557d090a

\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{apacite}
\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
%\usepackage{setspace}
%\doublespacing
\usepackage{graphicx}
%\graphicspath{ {graphics/} }

% Keywords command
\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
% Quotation command
\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}

\title{Thesis Draft}
\author{Mustafa İlhan}

\begin{document}
\maketitle

%%%
%%%
%%%
\begin{abstract}
In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored (or researched). Why and how are they used by the artist? Are there any differences with the original items compared to discarded items? (In other words using has using discarded materials or trash specific (or special) meaning and message?) This is a work to explore the re-usage of trash in artworks (place or the role in the art practice). (and also in which scope? medium, message, life practice\ldots)

Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making. The process effects how one's lives and lifestyle. (But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.)

With the help of art discarded thing can be find a place in the society. This issue is examined through the trash which is discarded by the society. By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life. The relationship between value creation and artistic practice examined through the artworks that uses trash as medium and representation.

From periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible. Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them. In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated. Stages and expression of this practice is examined with my artwork in the context of art.

\textbf{Driving questions} Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again.

\textbf{Statement.} With the help of art discarded things ---in the scope of thesis trash especially paper trash--- can be transformed beyond the other industrial (or technological) methods.

\textbf{Statement.} Using trash can not only understand in ecological perceptions, it also have powerful political claims. Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.  
\end{abstract}
\keywords{trash, art, value creation, transformation}

@@

%
\subsubsection{Perspectives related with trash from different disciplines}
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it handled by generally by the municipals. 
\end{itemize}

@@

%
\subsubsection{Comparison of trashes}
The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages.

@@

%
\subsubsection{Types of trashes}
Different production process generates different types of trash. According to production process, decomposition process\ldots

@@

%%
%%
\subsection{What might be the meaning of using trash as a medium in the artworks? Questioning trash as a medium for artist}
\begin{itemize}
\item Some works try to raise awareness the problems that are the result of trash. (It treats environment and nature.)
\item Some of them reflect people's lifestyle especially throw away culture. As a mirror of current lifestyle.
\item Try to find a new value and meaning from the discarded material that are useless anymore. To explore a new approach, new way. Subvert people's ideas about trash and their attitudes by turning materials to the something meaningful (or valuable). Trash to treasure.
\item Using discarded item to represent other discarded things by the ruling ideology or approach. For example, trash can be used to represent refugees. The things that we are trying to discard does not mean that they have no value, instead it means that we have no ability to reveal its potential. In other words, refugees have potential but we see them as players that will change our current system. Therefore, it can be said that willing to transform trash to treasure is to require change of current lifestyle. Rejecting discarding something especially thing that you get value from it is a process and spread through to the ones life.
\item One way is not to produce trash. (Zero trash philosophy.) The other one is to transform trash into something else.
\item What type of experience is that collecting and working on objects that are generally discarded? Experiencing out of common practice, being open to new explorations.
\item Instead of a world that produce trash, how could it be a world created from trash?
\item Combining industrial goods with objects transformed from trash is another way to find a place to trash in the community. It also signifies that trash still has a good quality to used with new materials. Creating composite products from new and reused items. Using the valuable thing with the invaluable thing. It becomes more valuable or less valuable. Depends on the perception.
\item Aesthetics of trash. Revealing aesthetics value of discarded stuff. (Unique visual value. Trash portraits, sculptures etc.)
\end{itemize}

@@

%%%
%%%
%%%
\section{Collage, Assemblage and the Found Object}
In this chapter root of using objects in the artworks is examined. Using objects on artworks beyond their intended purpose. Developing artworks not only painting but also using paper and other stuff by pasting them together.

%%
%%
\subsection{Collage}
Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or “found” materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions. Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.

\cite{greenberg1984collage}

%%
%%
\subsection{Assemblage}
Assemblage work produced by the incorporation of everyday objects into a composition. It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional. Diverse range of things can be used production of work. In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art. William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.

%%
%%
\subsection{the Found Object (Ready-mades)}
Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function. Pablo Picasso first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912). Marcel Duchamp is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art. The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.

%%
%%
\subsection{\textit{Bricolage}}
Something constructed using whatever was available at the time.

Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \cite{levi1966savage}

%%
%%
\subsection{Folk Art}
In contrast to fine art, folk art is primarily utilitarian(practical and functional, not just for show) and decorative rather than purely aesthetic. The nature of folk art is specific to its particular culture.

%%
%%
\subsection{Art and activism}

%%
%%
\subsection{History of Consumption and Waste}
"The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}

%%
%%
\subsection{Discussion}
Are artworks made from trash just examples of collage and assemblage or more than from them? What about the experience and interaction with other people? Turning art making process to a life practice (or part of life) can be explained in the context of collage (which is mainly related with how a 2d canvas created). But all of them work in fragments, combine many objects together.

Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.

In the world of computer science, the term garbage also refers to situations of loss in which data or objects in memory go unused in computer operations.

%%%
%%%
%%%
\section{Artworks}
Artist and artworks related with trash and their analysis. Stages of their works and methods.

% FROM ReVista
Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.

% FROM Paola Ibarra ReVista
Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere. Is there a limit to recycling and representation? Or is there a point at which waste cannot become art (or anything else)?

\begin{itemize}
% FROM Maite Zubiaurre, ReVista Garbage
\item Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement. It is that particular type of trash meet in the public places. trash left behind, trash on the sidewalk, squished, squashed, and weathered. Filomena Cruz sees trash that we don’t want to see. A
piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life. 
  \begin{figure}[ht]
      \centering
      \includegraphics[width=0.8\textwidth]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
      \caption{Road Kill by Filomena Cruz}
      \label{fig:FilomenaCruz_RoadKill_ReVista}
  \end{figure}

\item Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010)

% https://www.youtube.com/watch?v=sJxxdQox7n0
\item Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra,” or “Landfill Harmonic”.

% http://www.eloisacartonera.com.ar/ENGversion.html
\item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
urban pickers (\textit{cartoneros}) who pick it from the streets. Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]
  \begin{figure}[ht]
      \centering
      \includegraphics[width=0.8\textwidth]{graphics/EloisaCartonera_Books.jpg}
      \caption{Books covered by Eloisa Cartonera}
      \label{fig:EloisaCartonera_Books}
  \end{figure}

% FROM Paola Ibarra, ReVista
%\item Forever; Blue Yonder by artist Kyle Huffman
%\item Too Too---Much Much by Thomas Hirschhorn
%\item Autoconstrucción by Abraham Cruzvillegas
%\item Pictures of Garbage by Vik Muniz

% FROM Daniel Lind-Ramos BY LOWELL FIET, ReVista
%\item Daniel Lind-Ramos

% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
% https://www.youtube.com/watch?v=v6IoEF_Tsrw
\item Nick Quijano has some rules to create assemblages. \quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor. As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object. Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.

% FROM Burning Messages BY MICHAEL WELLEN, ReVista
%\item Antonio Berni

% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
\item Haiti case. When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage. It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city. When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No. When you have clean streets you have good health, and that is the most important thing.} (This is very strange. It shows that working with trash and being clean healthy is not a contradiction. Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.

% FROM Thinking on Film and Trash BY ERNESTO LIVON-GROSMAN, ReVista
% By the 1950s a film like Tire Dié (Fernando Birri, Argentina, 1956) already portrays the collecting, classifying and recycling of trash not only as a source of informal income but as a commercial activity linked to the formal economy. In these films, trash is not the end of a process of consumption but the beginning of a cycle of production. These movies share the idea that trash could be a departure point to think about the modern condition as defined by consumption, class disparities, contamination and urban development. The poet Charles Baudelaire is one of the first to make the connection between the rag picker and the modern city. Walter Benjamin picks it up and from then on the fragmentary condition of trash will remain associated with contemporary art and ultimately with the Modern condition: the industrial refuse could be redeemed by art. It is in this sense that filmmaking becomes allegorical and mimics the process of recycling when it reappropiates archival materials and found footage to create new narratives from scraps, fragments, of films that were not in any way connected to these new narratives.

\item Joseph Cornell

\item \textbf{American Beauty.} The film American Beauty , which features a long, poetic clip of a plastic bag swirling on an eddy of air, snagged five Academy Awards, yet I for one still find it hard to think of plastic bags as things of beauty.

\end{itemize}

Childs can enjoy with trash. I remember from my childhood, we collect crown cap and play with them. Some caps are found less and they worth more. We are looking everywhere for them. To make them flat we put them on the railways. After train passed we get perfect plat cap. At that time it is not trash for us. It has a value and part of our games and enjoy. To have fun a bunch of trash can be enough for us.

In the case of recycling, a dead objects, or an object that reached end of life will begin a new cycle of life. By the artist or other parts are give them a new life. They can reborn as a different things. Do people collect them aware of it? Discarded items unites together with the hands of a artist.

Trash is global topic men. When you talk about trash, everyone have ideas about it.

Think a city that has trash monument in the every corner. created from their trash. merged with the city life and gaining unique cityscapes and aesthetics. or think that a museum a trash museum. Exhibits works of art embracing the trash in all aspects. Maybe done by the artist or the visitors from all around world. A place for garbage other than a landfill. Waiting their creator to meet again. What a great idea isn't it? Meeting their creators again. But this time their creator can recognize their trash. They transformed to totally new thing. Reborn. Transformed (Kafka, Gregor Samsa).

%%
%%
\subsection{Artist statements}

%%%
%%%
%%%
\section{My Artwork/Project}
Here stages of my artwork are listed:
\begin{itemize}
\item \textbf{Memories.} As far as I know I collect things it is hard to say collecting started after an exact event or time but there are several memories that I remember. One of these (First of them) is from my primary school teacher. When I was third class my teacher give us a homework to bring colorful paper to make something(whatever it is I don't remember). The day after we bring some colorful paper but she did not. Instead of this she bring paper cut out from packages that are colorful, shinny and qualify. And I remember clearly that she suggest that same for us. Do not throw out packages, look for the useful parts and keep them to use later. 
\item \textbf{Motivation.} I can not throw them away. When I throw them I became sad for them. I have to find something useful for it. Even if I can not find it, I can pass it to another person who can make use of it for own purposes. We are humans that can produce, transform items. One of most developed species in the earth that produce and use tools. There is a lot of effort to produce thrown away and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception. 
\item \textbf{Collecting.} One of the most found trash in my habitat is paper. I work at METU Technopolis, live at 100. yil which is the nearest settlement to METU and study at Bilkent. People live there commonly use paper and needs paper. Paper is nearly everywhere. Reusing the paper is not limited with recycling of it. There is a another ways of it. When we recycle them actually we again send away them and use it as we all know. (industrial papers and notebooks.) There is no richness here. Same type of paper. Produced after a industrial process. I collected them from my friends (people that have communicate often). Sometimes I collect them from trash bins and roads. 
\item \textbf{Transforming.} I turned them to notebooks. Actually I use it for my self. And while I was using of it I am very proud of it. I am studying nearly more 20 twenty years and I have always need for notebooks and use them. It is some sort of passion for me notebooks. Because I always admire notebook beautifully design or uniquely designed. I collect them whenever I find and most of the time I only save them for later use. 
\end{itemize}

%%
%%
\subsection{Functionality and Art Debate}
From an art historical perspective, you could say that functional art is the inverse of Marcel Duchamp's famous readymades, where he transformed utilitarian objects---a urinal, a bottle rack, etc.---into conceptual artworks by fiat: it became art because he said it was. Duchamp's works kills the functionality. It works beyond the functional perception. Moves the debate to the conceptual frame. However it is not every time case. Today many functional art objects are as avidly acquired by collectors as their fine-art brethren, and are appreciated just as much for their beauty as their use value. Ancient Chinese vases, for example, while still capable of performing their originally intended function (displaying flowers), are prized for their historic and aesthetic value more than anything else. \quotes{In conceptual art,} Sol LeWitt writes, \quotes{the idea or concept is the most important aspect of the work\ldots The idea becomes the machine that makes the art} \cite{lewitt1967paragraphs}. Therefore anything can be turned to art with a good idea.

% TODO PRAP.
Comparing art to craft is like comparing philosophy to engineering: they're two separate ways of looking at the same thing. To me art is communication of an idea or an emotion, while craft is the physical manipulation of material. An object can easily be both, either, or neither. A sculpture, for example, may communicate, but it was constructed using craft. Likewise a teapot can communicate an idea, but it was crafted. Function is misleading and no distinction. Functional objects can still communicate ideas, so art can be functional. One object could be viewed two ways: if you look at the way it was made and the materials used, you are looking at its craft, if you think about its ideas, you are viewing it as art. An object could have been crafted, but contain no art. Even a painting can be crafted but artless. A ready-made might be art with no craft. I very much like the idea of a spectrum. One last thought: skill doesn't enter into the definition of art, since a piece could succeed as art but be poorly crafted.

%%
%%
\subsection{Paper}
"Paper is an indispensable product throughout the world. Its primary use is as a medium for writing, essential for bureaucracy, education, communications, information storage, and in the spread of information. In addition, it is used for the packaging for transport and convenience of a wide range of items from food to industrial equipment. Paper also has specific technological uses, such as for filters and in art, home furnishings, and architecture, and it has a range of uses for hygiene purposes. Paper in several forms is consumed on a daily basis by each person in the Western world." \cite{trafford2012paper}

%
\subsubsection{Environmental Impact}
Paper is both biodegradable and a renewable resource, which means in consumption and waste terms, its environmental impact is relatively small compared to the many more-toxic and bulky waste products that are found in everyday garbage. However, the chemicals, water, and electricity used in its manufacture are considerable---and these are nonrenewable resources---and certain types of chemicals used in paper production are toxic. In addition, if waste paper is sent to a landfill, it releases carbon dioxide emissions. Further, forest resources are not always as renewable as one may like to think. These environmental impacts can be greatly reduced by recycling (paper being one of the most easily and cheaply recyclable products in everyday use) and by conscientious consumption practices.

Paper made exclusively from wood is called virgin paper, while paper produced out of used paper that is re-pulped is called recycled paper. Recycling paper can greatly diminish demand for virgin fiber from wood. However, there will always be a demand for virgin paper because, although paper is thought of as a renewable resource, it cannot be recycled indefinitely. It can only be recycled four to six times, as the fibers get shorter and weaker each time. In addition, some virgin pulp must be introduced into the process each time to maintain the strength and quality of the fiber, so no matter how much is recycled, paper will always need some virgin fiber.

%
\subsubsection{History}
The word paper comes from papyrus, the plant that was first used for making a medium for writing in ancient Egypt.

%
\subsubsection{Production}
All types and qualities of paper share the same basic method of manufacture, including newspaper paper, print paper, and carton used for boxes.

%
\subsubsection{Uses}
Paper has become the most ubiquitous product in the age of information. Such products often complete their journey from shop floor to garbage in a single day; for example, newspapers, print paper, packaging, lavatory paper, tea bags, transport tickets, price tags, shopping bags, flyers, leaflets, wrapping paper, napkins, and tissues.

%%
%%
\subsection{Why (package) paper?}
Easy to collect. Easy to find. Thrown out even if it is good quality. Packaging materials are very widespread. Appropriate for painting and writing.

%%
%%
\subsection{Why covering notebooks and books?}

%%
%%
\subsection{Why giving away?}
Aim is to spread the idea by making something useful from trash. Increase diversity, activate (or encourage) people to embrace the trash.

%%
%%
\subsection{Why in the public space?}
To reach more audience. Actually the audience is out of the art galleries. They are walking in the streets. Putting them to next to people is much more effective. It is not visible and nearly it is hided from society. It is dirty. Removed from the society. There is a effort to hide them away. However in this project it is again showed to the society. Because it is revisited and reclaimed.

%%
%%
\subsection{Artistic tactics}
Here I followed some tactics to realize my purposes. I called them artistic tactics. Easy to carry while traveling. Small notebooks. Placing them to their routes.

\subsection{Why is it art?}
Uses artistic methods? Does it represent anything? The idea is transforming things. Anything can be transformed and re-contextualized again. The limitation is our imagination and approach. It has a claim. In can be analyzed and examined in the context of art. It is hard to say that something is art or not. However it can be examined in the context of art. There are artworks reject art galleries. There are artworks also reject commodities. It has purpose that. spread out the idea in different manner. Subverts peoples ideas.

The work aims to liberate the imagination and change the way people see the trash.

@@

%%
%%
\subsection{Trash Aesthetics}
Walter Benjamin's trash aesthetics and Adornos reflection.

%%%
%%%
%%%
\section{Sample Phrases}

\bibliographystyle{apacite}
\bibliography{ref}

\end{document}

>>>>

\chapter{Theory of Trash}

@@

%
\subsubsection{Perspectives related with trash from different disciplines}
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it handled by the municipals generally.
\item Technological perspectives
\end{itemize}

@@

%
\subsubsection{How does it become(turn to) art?}
How does it draw attention of artist, and also mine?

%
\subsubsection{Types and Comparison of trashes}
The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages.

@@

Different production process generates different types of trash. According to production process, decomposition process\ldots

@@

@@

@@

%%
%%
\subsection{Trash Aesthetics}
%Walter Benjamin's trash aesthetics and Adornos reflection. 
\quotes{Benjamin’s approach to history is through ‘trash’---through the spent and discarded materials that crowd the everyday}  \cite{highmore2002thrashaesthetics}. Benjamin’s importance as a theorist of the everyday is most evident in his attention to the everyday experiences of modernity. In the face of the endless proliferation of trash, Benjamin potentially suggests a ‘trash aesthetics’ that could be used radically and critically to attend to the everyday. The method might be thought of in terms of ‘recycling’ – an ecology of everyday experience.

% HERE Same sample phrases are listed you can use them:

% The artist thinks, acts, performs music, and writes outside the framework that society has created.

% In an effort to expand art activism's capacity to create real social change, this article will (1) examine the theoretical framework behind art activism and art's efficacy in accessing emotional pathways; (2) explicate ways to strategically approach art activism through the use of specific case studies; and (3) explain one practical form of art activism-theater-based conflict resolution-that is transforming the ways communities are addressing social injustice.

% Outline:
% Weak points:
% Where to study next.
